\section{Introduction}
Asset management is an important problem is many industries.  Asset management typically involves tracking 
the location of materials from the factory, to the warehouse, to the customers who purchase the item.
There's a bunch of work on system that perform this tracking~cite{}.  The general formulation of the problem
involves a set up of known locations and uniquely identifiable object.  When the object moves from one location
to another, the arrival time is record along with the object identifier.  In most cases, both the arrival and
departure time is recorded.  When the item is purchases, the customer identifier is associated with the object
identifier.

Buildings consume 40\% of the energy produced in the United State and about 30\% of that is consumed by plug-loads
in the building.  Given the nature of plug-loads -- hundred of distributed, personal, mobile energy-consuming
objects in the building -- it is difficult to track and understand how they are used and therefore it is difficult
to formulate a reduction strategy for this portion of building energy consumption.  The problem here is similar
to the generalized asset management problem, with the addition of object state.  What is the energy consumption
of the 4th floor of this building?  How does it compare to yesterday?  The generalized form appears in other contexts
as well.  For example, hospitals need to track where they stuff is and how many times it's been used because some
items have a rechard cycle that's closely correlated with the usage count.
