\chapter{Sensing in the Built Environment}

% \section{Metadata And Context Extraction}

% \section {Geometric, Functional, and Interactive Relationships}

% \section{Modeling Interaction From Geometric, Functional Information}

% \section{Verifying Geometric and Functional Relationships From Empirically-Inferred Interactions}

% \section{Evolution of the Built Environment}

% \section{Building Applications}

\section{Background}
Buildings consume nearly 40\% of the total energy produced in the United States and 72\% of the electricity.  Similar figures 
have been recorded in other industrialized countries~\cite{buildings_study}.  Furthermore, studies show that they waste from
30-80\% of the energy they consume.  With specter of global warming and the continued decrease in the cost of storage and 
communication, buildings have become a major target for improved energy efficiency.


\section{Building Information Systems}
Nearly three-quarter of building 100,000 square feet or larger, have a building management system (BMS) installed.  
A BMS typically consists of thousands of sensors, distributed through the internal spaces in the building, periodically reporting 
the state of the environment and the health of the individual sub-systems.  Their primary use is to maintain and diagnose problems
in throughout the building, as they are reported to the building manager.  However, recent interest in energy has motivated the 
expanded use of their data-gather capabilities in order to uncover opportunities to improve their overall performance, increase the
lifetime of the building, and make buildings more comfortable its occupants.

The suite of software available to contractors and architects is quite fast.  Ranging from pure simulation engines, such as 
DOE-2~\cite{doe_2} and EnergyPlus~\cite{eplus} to offline analytical packages that combine the strength of statistical analysis
with building models~\cite{osisoft}.

\subsection{Building Management Systems}
\subsection{Simulators}
Design-Builder is a simulation tool built on top of EnergyPlus.  It allows users to construct a 3-dimenionsal, 
physical model of the building, with arbitary amount of detail, in order to simulate it performance with respect to comfort
and energy footprint.

Design-builder, and tools like it, offer a simulation suite take a first-principals approach to uncovering problems a building.
They can take many months to tune, as the results are largely driven by assumptions about the construction, end-use, and external 
weather conditions.  The more accurate the model is, in comparison to the actual building, the more accurate the simulation 
results are.


\section{Building Applications Today}
The notion of applications in building has been around for some time, but almost exclusively in research.  The bulk of commercial
applications revolve around better visualization of building data through the web.  Recently~\cite{andrew_lighting, buildsys1, buildsys2},
there has been to work to expand the notion of building applications to include both visualization \emph{and} control.  Visualization, itself,
has broadened its reach to include personalized, aggregate, real-time views of energy consumption.

\subsection{Code Compliance}
The primary use of simulators on the market, is for code compliance.  There are building codes that are mandated by each state and across
the nation, that dictate the construction and health of newly constructed buildings.

\subsection{Energy Auditing}
Energy auditing is now seen like an application in buildings.

\subsection{Retrofitting}
Retrofits refers to the addition of new technology or the replacement of old technology to improve the performance of a system.  In the case
of buildings, this means improving some aspect of the construction of the building in order to improve its performance.  Often, simulations
are used to test the effects of retrofits in simulations and made decisions about whether or not to invest in a retrofit.  For example, 
the physical construction and replacement of the windows, the addition of sky lightings, the addition or replacement of HVAC components, are
all examples of retrofits that can be tested in simulation before they are purchased.


%\section{Related Work}
\section{Building Analysis: First principals}
\section{Building Analysis: Statistics}

\section{Shortcomings in Analytical Systems and Methodology}

\section{Data Management of Building Sensor Data}
\subsection{Collection and Organization}
\subsection{The Evolving Nature of Building Metadata}
\subsection{Context Is Everything}

\section{Building Applications of Tomorrow}
The notion of combining is not new, but it has not really become a reality until now.  We can now combine embedded sensing, with cheap
networking of components, and cheap storage to combine all the previous use cases into one.





% \begin{quote}
% Ugh servant Eulerian knowledge Prexy Lyman zig wiggly.  Promenade
% adduce.  Yugoslavia piccolo Exeter.  Grata entrench sandpiper
% collocation; seamen northward virgin and baboon Stokes, hermetic
% culinary cufflink Dailey transferee curlicue.  Camille, Whittaker
% harness shatter.  Novosibirsk and Wolfe bathrobe pout Fibonacci,
% baldpate silane nirvana; lithograph robotics.  Krakow, downpour
% effeminate Volstead?
% \end{quote}

% \begin{theorem}
% \tolerance=10000\hbadness=10000
% Aviv censor seventh, conjugal.  Faceplate emittance borough airline.  
% Salutary.
% \end{theorem}



% \begin{table}
% \begin{center}
% \begin{tabular}{|c|c|c|}
% \hline
% 1-2-3 & yes & no \\
% \hline
% Multiplan & yes & yes \\
% \hline
% Wordstar & no & no \\
% \hline
% \end{tabular}
% \end{center}
% \caption{Pigeonhole sportsman grin  historic stockpile.}
% \end{table}


% \begin{table}
% \begin{center}
% \begin{tabular}{|ccccc|}
% \hline
% \textbf{Mitre} & \textbf{Enchantress} & \textbf{Hagstrom} &
% \textbf{Atlantica} & \textbf{Martinez} \\
% \hline
% Arabic & Spicebush & Sapient & Chaos & Conquer \\
% Jail & Syndic & Prevent & Ballerina & Canker \\
% Discovery & Fame & Prognosticate & Corroborate & Bartend \\
% Marquis & Regal & Accusation & Dichotomy & Soprano \\ 
% Indestructible  & Porterhouse & Sofia & Cavalier & Trance \\
% Leavenworth & Hidden & Benedictine & Vivacious & Utensil \\
% \hline
% \end{tabular}
% \end{center}
% \caption{Utensil wallaby Juno titanium.}
% \end{table}

% \begin{figure}
% \[ \begin{picture}(90,50)
%   \put(0,0){\circle*{5}}
%   \put(0,0){\vector(1,1){31.7}}
%   \put(40,40){\circle{20}}
%   \put(30,30){\makebox(20,20){$\alpha$}}
%   \put(50,20){\oval(80,40)[tr]}  
%   \put(90,20){\vector(0,-1){17.5}}
%   \put(90,0){\circle*{5}}
% \end{picture}
%  \]
% \caption{Davidson witting and grammatic.  Hoofmark and Avogadro ionosphere.  
% Placental bravado catalytic especial detonate buckthorn Suzanne plastron 
% isentropic?  Glory characteristic.  Denature?  Pigeonhole sportsman grin.}
% \end{figure}


% sportsman grin\cite[page 45]{waveshaping} historic stockpile.
