\documentclass{ucbthesis}
\usepackage{biblatex}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}


\usepackage{amsmath,epsfig}
\usepackage{url}
\usepackage{xspace}
\usepackage{colortbl}
\usepackage{dsfont}
\usepackage{boxedminipage}
\ifx\pdfoutput\undefined
\usepackage[hypertex]{hyperref}
\else
\usepackage[pdftex,hypertexnames=false]{hyperref}
\fi

\usepackage{amssymb}
\usepackage{wasysym}

% \usepackage{caption}

\usepackage[caption=false,font=footnotesize]{subfig}
%\usepackage{subfigure}

\DeclareMathOperator{\median}{median}
\DeclareMathOperator{\dis}{d}
\DeclareMathOperator{\mad}{MAD}


% Double spacing, if you want it.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
 \usepackage{indentfirst}

%\newtheorem{theorem}{Jibberish}

\bibliography{references}

\hyphenation{mar-gin-al-ia}

\begin{document}

% Declarations for Front Matter

%\title{Metadata Management and Empirical Validation in the Built Environment Through Embedded Sensing}
\title{A Framework for Sensor Data Processing and Empirical Verification \\for the Built Environment}
\author{Jorge Jose Ortiz}
\degreesemester{Fall}
\degreeyear{2013}
\degree{Doctor of Philosophy}
\chair{Professor David E. Culler}
 \othermembers{Professor Randy H. Katz \\
    Professor Paul Wright}
\numberofmembers{3}
\prevdegrees{B.S. (Massachusetts Institute of Technology 2003 \\
  M.S. University of California, Berkeley 2010}
\field{Computer Science}
\campus{Berkeley}

% For a masters thesis, uncomment (remove the % at the beginning of)
% the following line.  This affects the title and approval pages,
% which by default calls this a "dissertation", not a "thesis".

%\itsamasters

% The title page generated by LaTeX is now acceptable for handing in.
% (This was not always the case).

\maketitle
\approvalpage
\copyrightpage

\include{abstract}

\begin{frontmatter}

\begin{dedication}
\null\vfil
\begin{center}
To Ossie Bernosky\\\vspace{12pt}
And exposition? Of go. No upstairs do fingering. Or obstructive, or purposeful.
In the glitter. For so talented. Which is confi∫nes cocoa accomplished.
Masterpiece as devoted. My primal the narcotic. For cine? To by recollection
bleeding. That calf are infant. In clause. Be a popularly. A as midnight
transcript alike. Washable an acre. To canned, silence in foreign.
\end{center}
\vfil\null
\end{dedication}

\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables

\begin{acknowledgements}
I want to thank my advisor for advising me.
\end{acknowledgements}

\end{frontmatter}

\pagestyle{headings}

% (Optional) \part{First Part}

\chapter{Introduction}
\section{Physical and Pervasive Computing}
\section{Computing As a Service}
\section{The Built Environment}
\section{Pervasive Computing Applications in Buildings}
\section{Research Statement And Hypothesis}
\emph{What are the architectural components and technical challenges in the design of an information system
that enables new and supports old classes of applications in the built environment?}  Given the emerging applications in
the built environment it is clear that the old information system design is not sufficiently open, flexibile, nor
scalable enough to support them.  Old information systems are tightly integrated from the field-level sensor to
the central supervisor control system.  There are two integration points in traditional systems that we argue 
are either fundamentally flawed or insufficient for emerging applications.  We describe the components that 
currently exist and identify those that are missing.  We show how these components/services enable emerging applications.  We also
discuss the technical challenges that must be solved in order to provide the correct semantics for these services.
Furthermore, we discuss a component that is fundamental for providing correct information to applications 
and formalize the notion of verification in the context of the built environment.  We provide several algorithmic 
solutions to these problems, which lay the foundation for a fundamental service in the broader architecture.

\section{Thesis Roadmap}
It start here and ends there.

\include{chap1}
\include{chap2}
\include{chap3}
\include{chap4}
% \include{chap5}
\include{chap6}
\chapter{Lessons Learned and Future Work}
\chapter{Conclusion}

% \appendix
% \chapter{More Monticello Candidates}

\printbibliography

\end{document}
