\chapter{Sensing in the Built Environment}
\label{chap:SensingInBuiltMain}

% Buildings consume nearly 40\% of the total energy produced in the United States and 72\% of the electricity.  Similar figures 
% have been recorded in other industrialized countries~\cite{buildings_study}.  Furthermore, studies show that they waste from
% 30-80\% of the energy they consume.  

Building management systems contain hundreds to thousands of sensors embedded in the systems that control the internal environment and
the spaces occupied by people.  There are many different kinds of sensors take a diverse set of physical measurements.
Some of them include temperature sensors in the thermostats,
valve-position sensors and actuators in the pipes, pressure sensors in the vents, temperature sensors on the vents and pipes as well, etc.
The BMS presents these through a graphical interface for building managers.  The graphical interface contains graphical sketches
of the systems and spaces in the building with icon images of the sensors in their approximate physical location represented
in the sketch.  The image sketch is generated from building schematics, so the interface is representative at the time of construction.
Building managers can quickly locate any sensor in the building through a series of clicks.

% that is giving bad readings or find the sensors that support
% a space where complaints are coming from, so that he/she could identify faulty readings through close inspection.
% The interface also allows them to visually inspect and quickly try to diagnose a problem, typically in response to occupant
% complaints.

Although BMS's have, to some degree, been an effective tool for centralized mangement of buildings, they lack the extensibility
and analytical capabilities necessary to support an ecosystem of tools for analyzing the building.  In general, software
practices in the building are non-standardized and non-systematic.
% Although BMS's have been revolutionary from a building management perspective, they lack many fundamental components for
% the kind of analysis that is needed to understand the building's operation over time.
% is performing now  
% and will perform in the future.  
% Also, building practices for software-driven building systems serve more as guideline than
% as a standard.  Naming, access, and organization of building data varies as much as buildings do.
This presents major challenges with respect to software re-use and scalability.  
In this thesis we discuss how we address these challenges through architectural design choices and analytical metholodology.  
The achitectural choices reconstruct the software layer that sits on top of existing building management systems and presents
a unified interface and standard API for analytical and control building applications.
The analytical methodology offers a general approach for verifying the construction of point names -- the naming scheme for 
sensors distributed throughout the building.  
% Both set a foundation for ongoing and future work.

The thesis is presented in the context of BMS systems and the building applications we aim to support.
% building systems and building-related applications.  
% We draw out the components in our analysis and design and discuss where it fits in the broader context of prior, computer-science related
% literature.  
In the next section, we describe the state-of-the-art practices followed by vendors of building information systems.
We describe the architectural features and design principals both implicitly and explicitly implemented into them.
We also present the pros and cons of these decisions and their implications and include a high-level description of our approach.
% Later chapters delve more deeply into the implications of our design decisions.

\input{SensingInTheBuiltEnvironment/IntegratedBMS}
\input{SensingInTheBuiltEnvironment/SupervisoryCtrlToApps}
\input{SensingInTheBuiltEnvironment/BMSShortcomings}
\input{SensingInTheBuiltEnvironment/AddressingBMSShort}
\input{SensingInTheBuiltEnvironment/ContextAccuracy}
\input{SensingInTheBuiltEnvironment/Summary}

