\section{Verification through Sensor Data}
% Verification is a broad topic in buildings that refers to verifying several things about building sensor metadata or through
% the sensor data.  Both cases are related to physical states are relationships that are assumed by the user and are either
% true and empirically observable or not.  If not, the end user or process should be informed and that inconsistencies should
% be immediately addressed.  This is even more of an issues as building begin to reply more and more on software.

% In this section we introduce some of the tools that we use for verification as discuss the 4 types of verification
% that exists in buildings.  We also present an overview approach for 3 of them.

Every system that manages data in the building specifies the building model manually at some point in the lifecycle of
the metadata.  Moreover, as the building changes and physical configuration of the building and deployment change,
all changes in the virtual representation of the building are updated manually.  As we move more and more towards
software controlled spaces and system that rely on accurate state capture of the physical environment, it becomes 
of highest important to automate the process that verifies correct configuration specification.

In the architecture we propose we see it as a concurrent process that will be in parallel with all active deployments.
The hierarchical naming scheme explicitly informs the verification process of ``group-by'' relationships between sensors.
Such ``group-by'' relationships typically specify physical relationships, such as grouping sensors that are in the same 
room in the same group, or the same floor in the same group.  Ideally, a verification process could perform several clustering
algorithms, using the empirical data collected from the sensors, to infer such physical relationships.  Most importantly,
it can alert the user when previously statistically clustered sensors no longer show the same \emph{inter-relationship}.

In this chapter, we discuss the analytical underpinning for a verification mechanism that could eventually become a 
component in the StreamFS -- or any other -- building software system.  We introduce the various kinds of verification in depth,
discuss the mathematical tools that help us both formulate and solve related verification problems, and present
results for the empirical verification of various physical relationships between sensors.  In the next section we discuss the various
types of verification, then we describe the tools, methodologies, and results for solving each.

\input{FilesystemMetaphoreNamingVerify/VerificationTypes}

