\section{Queries: Graphical, historical, histgraphical?}
The building can be represented as a collection of objects and the inter-relationship between them.

Typically the vocabulary is unknown, only general descriptions tend to be known beforehand.  We expose the inter-relationships
through hierarchical naming and symbolic links.  We also also allow arbitrary tags on the nodes.  These can be used to 
support general name search and queries based on general descriptions.
For example, a building analyst may want to know how many occupants were the chillers in the building or
to compare the relative occupancy load handled by the chillers versus the heaters, without having knowing specifically
which how each chiller/heater is physically connected to each space in the building and without knowing exactly when/where
each occupant was throughout the day.
Another, perhaps even more important query, is one related to mobile sensors -- i.e. ambient sensors on a mobile 
phone carried by occupants.  What's the distribution of temperature for the chillers versus the heaters, as experienced
by the occupants throughout the day.

Lets take an example in a different domain.  We could imagine a mobile environmental sensing application that associates individuals
with different locations (based on coordinate-based boundary conditions) as you walk around and passively collect environmental
readings, such as sound, light, Co2, temperature, etc.  A example query in this domain is ``what is the average Co2 level
in location 1 from time 1 to time 2?'' or ``what's the path with the smallest polution between location 1 and location 2 between time 1 and
time 2?''.

In manufactoring applications tracking context and associations over time is also necessary.  They ask questions like 
``which batches of powder are being used to form the ceramics at the heart of the batteries, how high a temperature is being used to bake them, how much energy is required to make each battery, and even the local air pressure.''~\cite{intman}.  In some cases, there is only a single
power meter taking measurement for a multi-stage machine with other sensors at each stage.  A related energy question, then, is 
what's the total power drawn by this machine for a specific batch of widgets -- requiring a search through the database to deduce
an indirect relationship between the meter and the widget over a certain time interval.

In a traditional database, these would have to be constructed iteratively.  We would have to determine the equipment and sensors involved, 
and their inter-relationship.  We would have to determine when that relationship existed and for how long and use those intervals 
to fetch the associated sensor readings for processing.  The implication for each is that a relationship history is maintained \emph{along with}
timeseries data produced by sensors.  In addition, this process implies the need for the end-user to know the names of the devices in order
to query for them explicitly, since the relationship between the equipment, the sensors, and other objects is a uniquely component in
the aggregate analysis.