

% \section{Process Management and Scheduling}
% \label{chap:ProcMngtSchedMain}

This chapter focuses are StreamFS mechanisms for process management, scheduling, piping, and gives details about
the filesystem abstraction and naming.
Processing of sensor data is a fundamental component of any analytics engine.  Sensor data is often dirty~\cite{4160603} and
must be cleaned before sophisticated processing jobs can consume it.  
In this chapter we discuss the details of our process manager and process scheduler.  We describe how our process manager handles
both internal and external processes and manages the buffers for all the jobs.  We give a detailed description of the job-specification
API and describe how the user interacts with StreamFS in order to activate, management, and de-activate jobs.  We also 
describe a class of applications that require the freshest data and present a new algorithm for providing the freshest set of data
points to those jobs, in a timely fashion.

This chapter also describes the use of the filesystem abstraction for representing streams in space.  The filesystem naming convention
provides a a unified namespace to applications for accessing physical resources and streams.  Moreoever, we support multi-naming through
symbolic links -- an important requirement for building applications. 

% Sensor data is fundamentally challenging to deal with because much of it must be cleaned before it can be processed.  For example,
% it is not uncommon to receive readings that is out of operational range, that is erroneous with respect to the previous observed trend,
% or to stop receiving readings altogether.  This implies the need for processing jobs to provide a level of filtering over the raw streams.
% Once the data is cleaned, it is typically consumed more sophisticated processes that aggregate the information or use it for control
% of the space or equipment.  We provide the mechanisms for handling both classes of processing jobs with our process management layer.
% In the next section we will discuss our process management layer and how users can both submit jobs to StreamFS for management or link
% their own external processing elements so that they can be managed through StreamFS but run outside of StreamFS.

% \input{ProcessMngt}
\input{ProcessManagementAndScheduling/ProcMngt}
\input{ProcessManagementAndScheduling/InternalProcs}
\input{ProcessManagementAndScheduling/ExternalProcs}
\input{ProcessManagementAndScheduling/DataFreshness}
\input{ProcessManagementAndScheduling/results}
% \input{ProcessManagementAndScheduling/summary}


